%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{ #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Aman Singh} & Email : \href{mailto:singh.amansingh935@gmail.com}{singh.amansingh935@gmail.com}\\
  \href{https://www.linkedin.com/in/amansinghseo/}{LinkedIn},
  \href{https://www.goodreads.com/user/show/88716452-aman-singh}{Goodreads},
  \href{https://github.com/aman935}{Github}
  & Mobile : +91-8629015159 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {IIT Mandi}{Mandi, Himachal Pradesh}
      {Bachelor of Technology in Computer Science and Engineering}{Aug. 2015 -- Jun 2019}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Daloopa.ai}{Noida}
      {Software Engineer-III; Python, , Django, Poetry, Docker, REST APIs, AWS, Redis, Celery}{Mar 2021 - Current}
      \resumeItemListStart
        \resumeItem{}
          {Handled metadata generation for our high-level data for clients by processing database objects and validating the financial models.}
        \resumeItem{}
           {Responsible for maintaining external facing REST-endpoints which enable data-transfer between our high-priority clients.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Amazon}{Bangalore}
      {Software Development Engineer; Java, Spring MVC, AWS, Microservices, Python}{June 2019 - March 2021} \newline
      \resumeItemListStart
    \resumeItem{}
          {Worked on customer-facing features like comparison table on product detail page, and adding logic for displaying icons in trust-widget.}
      \resumeItem{}
          {Enabled faster reporting of Installation Details to brands for contacting customers and reducing time between installations and delivery by around 4 hours.}
      \resumeItem{}
          {Improved code-quality within the team by standardising checkstyle rules for team-owned packages. Led the initiative to use this in further projects within the team.}
     \resumeItem{}
          {Worked on a project to develop a new API on an existing Micro-service to share and parse uber-level payment data to Product companies so they can provide better affordability options i.e. discounts/EMI options.}
      \resumeItem{}
          {Responsible for owning service which handles different aspects of pre-delivery experiences for heavy and bulky, high average sales value products, like confirming order by placing an IVR call.}
     \resumeItemListEnd
      
    
    \resumeSubheading
      {Amazon}{Bangalore}
      {SDE-Intern in Softlines team; ML; DNN, C++, Docker, Caffe, Jupyter Notebook}{Jun 2018 - Aug 2018}
      \resumeItemListStart
        \resumeItem{}
          {Implemented a Monomer model used for suggesting clothing and accessories that go-well together i.e. complementary recommendations. This was done by training the model on previous purchases by customers and predicting compatibility in new products.}
      \resumeItemListEnd
      
     \resumeSubheading
      {The Solar Labs}{Noida}
      {Software Development Intern; WordPress, Hosting Services, Domain management}{Jan 2018 - Feb 2018}
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
  \resumeSubItem{Music WebApp}
      {Made a music streaming webApp based on RubyOnRails with UI as a college project.}
  \resumeSubItem{The Solar Labs}
      {Setup the wordpress blog and worked on the Front-end for this solar startup which was also incubated in
IIT Mandi’s Catalyst.}
  \resumeSubHeadingListEnd

%-----------Awards-----------------
\section{Awards}
  \resumeSubHeadingListStart
    \resumeSubItem{2nd runner-up, Inter-IIT Tech Meet}
      {Voice controlled pick and place Arduino bot programmed in C++.}
    \resumeSubItem{3rd place}
      {in Avishkar at IIT Mandi for Anti-suicidal bot (out of 24 teams).}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Skills}
 \resumeSubHeadingListStart
    \resumeSubItem{Languages}{:Java, C, C++, Python}
    \resumeSubItem{Technologies}{{\latex}{\LaTeX\xspace}
, Dynamo DB, Amazon S3, AWS, Spring, SNS, SQS, Django, Docker, Caffe}
 \resumeSubHeadingListEnd
 
%--------EXTRACURRICULARS------------
\section{Extracurriculars}
 \resumeSubHeadingListStart
    \resumeSubItem{Programming Club}{
• Programming Club : Core team member. Responsible for taking classes on topics related to data structures and algorithms for college freshers. Organising hackathons and other club events.(2015-17)}
    \resumeSubItem{Guidance and Counselling Cell}{Responsible for mentoring multiple freshers, guiding and managing their orientation..(2016-17)}
 \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}

